---
title: "Study 2 (revised analysis July 2020)"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    theme: flatly
    toc: true
    toc_float: true
---

In Study 2, adults from the general population, as well as a smaller sample of charismatic evangelical Christians, were interviewed briefly about their spiritual experiences and their understanding of the mind. These interviews yielded one measure of porosity (“Porosity Scale”) and one measure of spiritual experience (“Spiritual Events” scale).

This notebook contains all of the analyses for Study 2 (revised July 2020).

```{r, message = F}
source("../scripts_general/dependencies.R")
source("../scripts_general/custom_funs.R")
source("../scripts_general/var_recode_contrast.R")
source("../scripts_general/data_load.R")
```

```{r}
require(stargazer)
detach("package:lmerTest")
```

```{r}
# custom function for substituting interaction symbol
sub_interact_fun <- function(str) {
  str <- gsub("\\`", "", str) # for `Porosity Vignettes`, etc.
  str <- gsub("\\.\\:", "\\. × ", str) # for country
  str <- gsub("\\:Sit", " × Sit", str)
  str <- gsub("\\:Rel", " × Rel", str)
  str <- gsub("\\:Pop", " × Pop", str)
  str <- gsub("\\:Por", " × Por", str)
  str <- gsub("\\:Abs", " × Abs", str)
  str <- gsub("\\:Gen", " × Gen", str)
  str <- gsub("\\:Age", " × Age", str)
  str <- gsub("\\:Edu", " × Edu", str)
  return(str)
}
```

```{r}
# show contrasts
contrasts(d2$country)
contrasts(d2$religion)
```

# Demographics

```{r}
d2_demo <- d2 %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age),
         # deal with subject_religion
         subject_religion = case_when(
           subject_religion %in% 
             c("7th Day Adventist",
               "A little Catholicism, pray Jesus",
               "Apostolic",
               "Baptist",
               "Catholic",
               "Catholic 5 times a year, don't study bible but large part of family make up.",
               "Catholicism",
               "Christian",
               "Christian Baptist",
               "Christian, raised Catholic",
               "christianity",
               "Christianity",
               "Christianity - possibly Presbyterian / Catholic, Raised Pentecostal",
               "Christianity, nondenominational",
               "Christians",
               "Christiantity",
               "Church of Latter Day Saints",
               "Culturally LDS",
               "Episcopalian",
               "Grew up Catholic",
               "ICGC Cape Coast Branch, Christianity",
               "Jehovah Witness", 
               "Jehovah's Witness",
               "LDS Latter Day Saints",
               "Methodist",
               "non denominational / Christian",
               "non-denominational",
               "Not specific type/denomination, parents bounced around, all Christian",
               "Orthodox Christian", "Pentecostal", "Pentecostal preacher",
               "Personal relationship w/ Jesus Christ", "Presbyterian",
               "Roman Catholic", "SDA (Christianity)",
               "Seventh Day Adventist Church", "True Jesus Church",
               "Unitarian Universalism", "United Methodist") ~ "Christian",
           subject_religion %in% 
             c("Actually believe in Buddhism",
               "Buddhism", "Buddhism (believe)",
               "Buddhism / Ancestors (a little bit believe)",
               "Buddhism, incline to deism",
               "Buddhism. Practice and has been vegetarian for 20 years",
               "Buddhist",
               "Buddhist (interviewed @ church)",
               "Incline to Buddhism", "Studying Buddhism",
               "Vipassana Buddhism",
               "Wat Baan Pong Kiang",
               "Wat Hua Deng", 
               "Wat Nong Ban") ~ "Buddhist",
           # subject_religion %in% 
           #   c("Family - Orthodox Jew / Jewish",
           #     "Judaism", "Orthodox Jewish") ~ "Jewish",
           subject_religion %in%
             c("Islam", 
               "Islam, but not believe anything", 
               "Islamic", 
               "Islamic Religion",
               "Muslim") ~ "Muslim",
           # subject_religion %in% 
           #   c("Hinduism") ~ "Hindu",
           grepl("agnost", tolower(subject_religion)) |
             grepl("atheis", tolower(subject_religion)) |
             grepl("don't", tolower(subject_religion)) |
             grepl("none", tolower(subject_religion)) |
             tolower(subject_religion) %in% 
             c("n/a", "no", 
               tolower("No (ex - JW) Partner Christian - Possibly Korean Baptist"), 
               "no religion", "no religion, finding one", "not really",
               tolower("Religion is a choice; I'm not interested in it.")) ~ "Agnostic/Atheist",
           subject_religion %in% c("missing data", "mdata", "NA") |
             is.na(subject_religion) ~ "Missing data",
           TRUE ~ "Other"),
         subject_urban_rural = recode(subject_urban_rural,
                                      "Urban" = 1, "Rural" = 0),
         religion = recode_factor(religion,
                                  "0" = "general pop.",
                                  "1" = "charismatic Chr."),
         agnostic_atheist = (subject_religion == "Agnostic/Atheist"),
         buddhist = (subject_religion == "Buddhist"),
         christian = (subject_religion == "Christian"),
         muslim = (subject_religion == "Muslim"),
         other = (subject_religion == "Other"),
         missing = (subject_religion == "Missing data"))
```

```{r}
d2_demo %>%
  group_by(country, religion) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_urban = mean(subject_urban_rural, na.rm = T),
            percent_affr = mean(subject_afford, na.rm = T),
            mean_ses = mean(subject_ses, na.rm = T),
            mean_religiosity = mean(subject_religiosity, na.rm = T),
            percent_christian = mean(christian, na.rm = T),
            percent_agnostic_atheist = mean(agnostic_atheist, na.rm = T),
            percent_buddhist = mean(buddhist, na.rm = T),
            percent_muslim = mean(muslim, na.rm = T),
            percent_other = mean(other, na.rm = T),
            percent_missing = mean(missing, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, Sample = religion,
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% urban` = percent_urban, `% can afford` = percent_affr,
         `Mean SES` = mean_ses, `Mean religiosity` = mean_religiosity,
         `% Christian` = percent_christian, 
         `% Agnostic/Atheist` = percent_agnostic_atheist, 
         `% Buddhist` = percent_buddhist, 
         `% Muslim` = percent_muslim, 
         `% Other` = percent_other,
         `[% Missing data]` = percent_missing) %>%
  mutate(Country = factor(Country, levels = levels_country),
         Sample = factor(Sample, 
                         levels = c("general population", "charismatic"),
                         labels = c("gen. pop.", "char. ev. Chr."))) %>%
  arrange(Country, Sample) %>%
  select(Country, Sample, n, `Age range`, `Mean age`, `% male`, `% female`,
         `Mean religiosity`,
         `% Christian`, `% Buddhist`, `% Muslim`, `% Other`, `% Agnostic/Atheist`,
         `[% Missing data]`,
         `% urban`, `% can afford`, `Mean SES`) %>%
  kable(digits = 2, align = c(rep("l", 2), rep("r", ncol(.) - 2))) %>%
  kable_styling(font_size = 16) # %>%
  # collapse_rows(1:2)
```


# Revised analyses (July 2020)

```{r}
d2_fortab <- d2 %>%
  mutate_at(vars(ends_with("_score"), subject_age), scale) %>%
  mutate(subject_hs = case_when(is.na(subject_education) ~ NA_character_,
                                subject_education == "No HS degree" ~ "no",
                                TRUE ~ "yes"),
         subject_hs = factor(subject_hs, 
                             levels = c("no", "yes")),
         subject_gender = factor(subject_gender, 
                                 levels = c("Female", "Male"))) %>%
  rename("Spiritual Events" = "spev_score",
         "Porosity Scale" = "por_score",
         "Country" = "country",
         "Population" = "religion",
         "Gender" = "subject_gender",
         "Age" = "subject_age",
         "Education" = "subject_hs")

contrasts(d2_fortab$Country) <- cbind(": Gh." = c(-1, 1, 0, 0, 0),
                                      ": Th." = c(-1, 0, 1, 0, 0),
                                      ": Ch." = c(-1, 0, 0, 1, 0),
                                      ": Va." = c(-1, 0, 0, 0, 1))
contrasts(d2_fortab$Population) <- cbind(": CC" = c(1, -1))
contrasts(d2_fortab$Education) <- cbind(": at least HS" = c(-1, 1))
contrasts(d2_fortab$Gender) <- cbind(": male" = c(-1, 1))
```

## Group differences

### Spiritual Events

```{r}
r01_spev <- lm(`Spiritual Events` ~ Country,
              data = d2_fortab)
r02_spev <- lm(`Spiritual Events` ~ Country * Population, 
              data = d2_fortab)
r03_spev <- lm(`Spiritual Events` ~ Country * Population +
                Gender + Age, # + Education, # missing data for ~50% of participants
              data = d2_fortab)
```

```{r, include = F}
# # run manually to check convergence
# summary(r01_spev)
# summary(r02_spev)
# summary(r03_spev)
```

```{r, include=F}
table_s2_diff_spev <- stargazer(r01_spev, r02_spev, 
                                r03_spev, type = "html",
                                ci = T,
                                report = c("vcsp"),
                                digits = 2,
                                digits.extra = 1000,
                                omit.table.layout = "n",
                                # order = c("^Country: ...$", 
                                #           "^Population: CC$", 
                                #           "Country", 
                                #           "Site"),
                                dep.var.labels.include = F,
                                dep.var.caption = "",
                                single.row = T)

cat(sub_interact_fun(table_s2_diff_spev), 
    file = "./stargazer_tables/table_s2_diff_spev.html")
```

### Porosity Scale

```{r}
r01_por <- lm(`Porosity Scale` ~ Country,
              data = d2_fortab)
r02_por <- lm(`Porosity Scale` ~ Country * Population, 
              data = d2_fortab)
r03_por <- lm(`Porosity Scale` ~ Country * Population +
                Gender + Age, # + Education,
              data = d2_fortab)
```

```{r, include = F}
# # run manually to check convergence
# summary(r01_por)
# summary(r02_por)
# summary(r03_por)
```

```{r, include=F}
table_s2_diff_por <- stargazer(r01_por, r02_por, 
                               r03_por, type = "html",
                               ci = T,
                               report = c("vcsp"),
                               digits = 2,
                               digits.extra = 1000,
                               omit.table.layout = "n",
                               # order = c("^Country: ...$", 
                               #           "^Population: CC$", 
                               #           "Country", 
                               #           "Site"),
                               dep.var.labels.include = F,
                               dep.var.caption = "",
                               single.row = T)

cat(sub_interact_fun(table_s2_diff_por), 
    file = "./stargazer_tables/table_s2_diff_por.html")
```

## Relationships

### Spiritual Events

#### Sample as fixed effect

```{r}
r04_spev <- lm(`Spiritual Events` ~ `Porosity Scale`,
               data = d2_fortab)

r05_spev <- lm(`Spiritual Events` ~ Country * Population * `Porosity Scale`,
               data = d2_fortab)

r06_spev <- lm(`Spiritual Events` ~ Country * Population * `Porosity Scale`
               + Gender + Age, # + Education, 
               data = d2_fortab)
```

```{r, include = F}
# # run manually to check convergence
# summary(r04_spev)
# summary(r05_spev)
# summary(r06_spev)
```

```{r, include=F}
table_s2_rel_spev_fixfx <- stargazer(r04_spev, r05_spev,
                                     r06_spev, type = "html",
                                     ci = T,
                                     report = c("vcsp"),
                                     digits = 2,
                                     digits.extra = 1000,
                                     omit.table.layout = "n",
                                     order = c("^`Porosity Scale`$"),
                                     dep.var.labels.include = F,
                                     dep.var.caption = "",
                                     single.row = T)

cat(sub_interact_fun(table_s2_rel_spev_fixfx), 
    file = "./stargazer_tables/table_s2_rel_spev_fixfx.html")
```


#### Sample as random effect

```{r}
r07_spev <- lmer(`Spiritual Events` ~ 1 
                 + (1 | Country/Population),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d2_fortab)

r08_spev <- lmer(`Spiritual Events` ~ `Porosity Scale` 
                 + (1 + `Porosity Scale` | Country/Population), 
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d2_fortab)

r09_spev <- lmer(`Spiritual Events` ~ `Porosity Scale`
                 + Gender + Age # + Education
                 # + (1 + `Porosity Scale` + Gender + Age | Country/Population), # NaN ranfx
                 # + (1 + `Porosity Scale` + Gender + Age || Country/Population), # perfectly correlated ranfx
                 # + (1 + `Porosity Scale` | Country/Population), # NaN ranfx
                 + (1 + `Porosity Scale` || Country/Population),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d2_fortab)
```

```{r, include = F}
# # run manually to check convergence
# summary(r07_spev)
# summary(r08_spev)
# summary(r09_spev)
```

```{r, include=F}
table_s2_rel_spev_ranfx <- stargazer(r07_spev, r08_spev,
                                     r09_spev, type = "html",
                                     ci = T,
                                     report = c("vcsp"),
                                     digits = 2,
                                     digits.extra = 0800,
                                     omit.table.layout = "n",
                                     order = c("^`Porosity Scale`$"),
                                     dep.var.labels.include = F,
                                     dep.var.caption = "",
                                     single.row = T)

cat(sub_interact_fun(table_s2_rel_spev_ranfx), 
    file = "./stargazer_tables/table_s2_rel_spev_ranfx.html")
```

```{r}
rsquared(modelList = list(r07_spev, r08_spev, r09_spev)) %>%
  mutate_at(vars(Marginal, Conditional), ~ round(., 2))
```

#### By country, sample as fixed effect

```{r}
r10_us_spev <- lm(`Spiritual Events` ~ Population * `Porosity Scale`,
                  data = d2_fortab %>% 
                    filter(Country == "US") %>%
                    mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                              ~ scale(.)))

r10_gh_spev <- lm(`Spiritual Events` ~ Population * `Porosity Scale`,
                  data = d2_fortab %>% 
                    filter(Country == "Ghana") %>%
                    mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                              ~ scale(.)))

r10_th_spev <- lm(`Spiritual Events` ~ Population * `Porosity Scale`,
                  data = d2_fortab %>% 
                    filter(Country == "Thailand") %>%
                    mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                              ~ scale(.)))

r10_ch_spev <- lm(`Spiritual Events` ~ Population * `Porosity Scale`,
                  data = d2_fortab %>% 
                    filter(Country == "China") %>%
                    mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                              ~ scale(.)))

r10_vt_spev <- lm(`Spiritual Events` ~ Population * `Porosity Scale`,
                  data = d2_fortab %>% 
                    filter(Country == "Vanuatu") %>%
                    mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                              ~ scale(.)))
```

```{r, include = F}
# # run manually to check convergence
# summary(r10_us_spev)
# summary(r10_gh_spev)
# summary(r10_th_spev)
# summary(r10_ch_spev)
# summary(r10_vt_spev)
```

```{r, include=F}
table_s2_rel_bycountry_spev_fixfx <- stargazer(r10_us_spev, r10_gh_spev,
                                               r10_th_spev, r10_ch_spev,
                                               r10_vt_spev, type = "html",
                                               ci = T,
                                               report = c("vcsp"),
                                               digits = 2,
                                               digits.extra = 1000,
                                               omit.table.layout = "n",
                                               # order = c("^`Porosity Scale`$"),
                                               dep.var.labels.include = F,
                                               dep.var.caption = "",
                                               single.row = T)

cat(sub_interact_fun(table_s2_rel_bycountry_spev_fixfx), 
    file = "./stargazer_tables/table_s2_rel_bycountry_spev_fixfx.html")
```

#### By country, sample as random effect

```{r}
r11_us_spev <- lmer(`Spiritual Events` ~ `Porosity Scale`
                    # + (1 + `Porosity Scale` | Population), # perfectly correlated ranfx
                    + (1 | Population), 
                    data = d2_fortab %>% 
                      filter(Country == "US") %>%
                      mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                                ~ scale(.)))

r11_gh_spev <- lmer(`Spiritual Events` ~ `Porosity Scale`
                    # + (1 + `Porosity Scale` | Population), # perfectly correlated ranfx
                    + (1 | Population), 
                    data = d2_fortab %>% 
                      filter(Country == "Ghana") %>%
                      mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                                ~ scale(.)))

r11_th_spev <- lmer(`Spiritual Events` ~ `Porosity Scale`
                    # + (1 + `Porosity Scale` | Population), # perfectly correlated ranfx
                    + (1 | Population), 
                    data = d2_fortab %>% 
                      filter(Country == "Thailand") %>%
                      mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                                ~ scale(.)))

r11_ch_spev <- lmer(`Spiritual Events` ~ `Porosity Scale`
                    # + (1 + `Porosity Scale` | Population), # perfectly correlated ranfx
                    + (1 | Population), 
                    data = d2_fortab %>% 
                      filter(Country == "China") %>%
                      mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                                ~ scale(.)))

r11_vt_spev <- lmer(`Spiritual Events` ~ `Porosity Scale`
                    # + (1 + `Porosity Scale` | Population), # perfectly correlated ranfx
                    + (1 | Population), 
                    data = d2_fortab %>% 
                      filter(Country == "Vanuatu") %>%
                      mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                                ~ scale(.)))
```

```{r, include = F}
# run manually to check convergence
summary(r11_us_spev)
summary(r11_gh_spev)
summary(r11_th_spev)
summary(r11_ch_spev)
summary(r11_vt_spev)
```

```{r, include=F}
table_s2_rel_bycountry_spev_ranfx <- stargazer(r11_us_spev, r11_gh_spev,
                                               r11_th_spev, r11_ch_spev,
                                               r11_vt_spev, type = "html",
                                               ci = T,
                                               report = c("vcsp"),
                                               digits = 2,
                                               digits.extra = 1000,
                                               omit.table.layout = "n",
                                               # order = c("^`Porosity Scale`$"),
                                               dep.var.labels.include = F,
                                               dep.var.caption = "",
                                               single.row = T)

cat(sub_interact_fun(table_s2_rel_bycountry_spev_ranfx), 
    file = "./stargazer_tables/table_s2_rel_bycountry_spev_ranfx.html")
```

```{r}
rsquared(modelList = list(r11_us_spev, r11_gh_spev, r11_th_spev, 
                          r11_ch_spev, r11_vt_spev)) %>%
  mutate_at(vars(Marginal, Conditional), ~ round(., 2))
```


#### By population, sample as fixed effect

```{r}
r12_gp_spev <- lm(`Spiritual Events` ~ Country * `Porosity Scale`,
                  data = d2_fortab %>% 
                    filter(Population == "general population") %>%
                    mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                              ~ scale(.)))

r12_cc_spev <- lm(`Spiritual Events` ~ Country * `Porosity Scale`,
                  data = d2_fortab %>% 
                    filter(Population == "charismatic") %>%
                    mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                              ~ scale(.)))
```

```{r, include = F}
# # run manually to check convergence
# summary(r12_gp_spev)
# summary(r12_cc_spev)
```

```{r, include=F}
table_s2_rel_bypop_spev_fixfx <- stargazer(r12_gp_spev, r12_cc_spev,
                                               type = "html",
                                               ci = T,
                                               report = c("vcsp"),
                                               digits = 2,
                                               digits.extra = 1000,
                                               omit.table.layout = "n",
                                               # order = c("^`Porosity Scale`$"),
                                               dep.var.labels.include = F,
                                               dep.var.caption = "",
                                               single.row = T)

cat(sub_interact_fun(table_s2_rel_bypop_spev_fixfx), 
    file = "./stargazer_tables/table_s2_rel_bypop_spev_fixfx.html")
```

#### By population, sample as random effect

```{r}
r13_gp_spev <- lmer(`Spiritual Events` ~ `Porosity Scale`
                    + (1 + `Porosity Scale` | Country), 
                    data = d2_fortab %>% 
                      filter(Population == "general population") %>%
                      mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                                ~ scale(.)))

r13_cc_spev <- lmer(`Spiritual Events` ~ `Porosity Scale`
                    + (1 + `Porosity Scale` | Country), 
                    data = d2_fortab %>% 
                      filter(Population == "charismatic") %>%
                      mutate_at(vars(`Spiritual Events`, `Porosity Scale`),
                                ~ scale(.)))
```

```{r, include = F}
# run manually to check convergence
summary(r13_gp_spev)
summary(r13_cc_spev)
```

```{r, include=F}
table_s2_rel_bypop_spev_ranfx <- stargazer(r13_gp_spev, r13_cc_spev,
                                               type = "html",
                                               ci = T,
                                               report = c("vcsp"),
                                               digits = 2,
                                               digits.extra = 1000,
                                               omit.table.layout = "n",
                                               # order = c("^`Porosity Scale`$"),
                                               dep.var.labels.include = F,
                                               dep.var.caption = "",
                                               single.row = T)

cat(sub_interact_fun(table_s2_rel_bypop_spev_ranfx), 
    file = "./stargazer_tables/table_s2_rel_bypop_spev_ranfx.html")
```

```{r}
rsquared(modelList = list(r13_gp_spev, r13_cc_spev)) %>%
  mutate_at(vars(Marginal, Conditional), ~ round(., 2))
```

