---
title: "Study 2"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    theme: flatly
    toc: true
    toc_float: true
---

In Study 2, adults from the general population, as well as a smaller sample of charismatic evangelical Christians, were interviewed briefly about their spiritual experiences and their understanding of the mind. These interviews yielded one measure of porosity (“Porosity Scale”) and one measure of spiritual experience (“Spiritual Events” scale).

This notebook contains all of the analyses for Study 2.

```{r, message = F}
source("../scripts_general/dependencies.R")
source("../scripts_general/custom_funs.R")
source("../scripts_general/var_recode_contrast.R")
source("../scripts_general/data_load.R")
```

```{r}
# show contrasts
contrasts(d2$country)
contrasts(d2$religion)
```

# Demographics

## Table S19

```{r}
d2_demo <- d2 %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age),
         # deal with subject_religion
         subject_religion = case_when(
           subject_religion %in% 
             c("7th Day Adventist",
               "A little Catholicism, pray Jesus",
               "Apostolic",
               "Baptist",
               "Catholic",
               "Catholic 5 times a year, don't study bible but large part of family make up.",
               "Catholicism",
               "Christian",
               "Christian Baptist",
               "Christian, raised Catholic",
               "christianity",
               "Christianity",
               "Christianity - possibly Presbyterian / Catholic, Raised Pentecostal",
               "Christianity, nondenominational",
               "Christians",
               "Christiantity",
               "Church of Latter Day Saints",
               "Culturally LDS",
               "Episcopalian",
               "Grew up Catholic",
               "ICGC Cape Coast Branch, Christianity",
               "Jehovah Witness", 
               "Jehovah's Witness",
               "LDS Latter Day Saints",
               "Methodist",
               "non denominational / Christian",
               "non-denominational",
               "Not specific type/denomination, parents bounced around, all Christian",
               "Orthodox Christian", "Pentecostal", "Pentecostal preacher",
               "Personal relationship w/ Jesus Christ", "Presbyterian",
               "Roman Catholic", "SDA (Christianity)",
               "Seventh Day Adventist Church", "True Jesus Church",
               "Unitarian Universalism", "United Methodist") ~ "Christian",
           subject_religion %in% 
             c("Actually believe in Buddhism",
               "Buddhism", "Buddhism (believe)",
               "Buddhism / Ancestors (a little bit believe)",
               "Buddhism, incline to deism",
               "Buddhism. Practice and has been vegetarian for 20 years",
               "Buddhist",
               "Buddhist (interviewed @ church)",
               "Incline to Buddhism", "Studying Buddhism",
               "Vipassana Buddhism",
               "Wat Baan Pong Kiang",
               "Wat Hua Deng", 
               "Wat Nong Ban") ~ "Buddhist",
           # subject_religion %in% 
           #   c("Family - Orthodox Jew / Jewish",
           #     "Judaism", "Orthodox Jewish") ~ "Jewish",
           subject_religion %in%
             c("Islam", 
               "Islam, but not believe anything", 
               "Islamic", 
               "Islamic Religion",
               "Muslim") ~ "Muslim",
           # subject_religion %in% 
           #   c("Hinduism") ~ "Hindu",
           grepl("agnost", tolower(subject_religion)) |
             grepl("atheis", tolower(subject_religion)) |
             grepl("don't", tolower(subject_religion)) |
             grepl("none", tolower(subject_religion)) |
             tolower(subject_religion) %in% 
             c("n/a", "no", 
               tolower("No (ex - JW) Partner Christian - Possibly Korean Baptist"), 
               "no religion", "no religion, finding one", "not really",
               tolower("Religion is a choice; I'm not interested in it.")) ~ "Agnostic/Atheist",
           TRUE ~ "Other"),
         subject_urban_rural = recode(subject_urban_rural,
                                      "Urban" = 1, "Rural" = 0),
         religion = recode_factor(religion,
                                  "0" = "general pop.",
                                  "1" = "charismatic Chr."),
         agnostic_atheist = (subject_religion == "Agnostic/Atheist"),
         buddhist = (subject_religion == "Buddhist"),
         christian = (subject_religion == "Christian"),
         muslim = (subject_religion == "Muslim"),
         other = (subject_religion == "Other"))
```

```{r}
d2_demo %>%
  group_by(country, religion) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_urban = mean(subject_urban_rural, na.rm = T),
            percent_affr = mean(subject_afford, na.rm = T),
            mean_ses = mean(subject_ses, na.rm = T),
            mean_religiosity = mean(subject_religiosity, na.rm = T),
            percent_christian = mean(christian, na.rm = T),
            percent_agnostic_atheist = mean(agnostic_atheist, na.rm = T),
            percent_buddhist = mean(buddhist, na.rm = T),
            percent_muslim = mean(muslim, na.rm = T),
            percent_other = mean(other, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, Sample = religion,
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% urban` = percent_urban, `% can afford` = percent_affr,
         `Mean SES` = mean_ses, `Mean religiosity` = mean_religiosity,
         `% Christian` = percent_christian, 
         `% Agnostic/Atheist` = percent_agnostic_atheist, 
         `% Buddhist` = percent_buddhist, 
         `% Muslim` = percent_muslim, 
         `% Other` = percent_other) %>%
  mutate(Country = factor(Country, levels = levels_country),
         Sample = factor(Sample, 
                         levels = c("general population", "charismatic"),
                         labels = c("gen. pop.", "char. ev. Chr."))) %>%
  arrange(Country, Sample) %>%
  select(Country, Sample, n, `Age range`, `Mean age`, `% male`, `% female`,
         `% Christian`, `% Buddhist`, `% Muslim`, `% Other`, `% Agnostic/Atheist`,
         `% urban`, `% can afford`, `Mean SES`, `Mean religiosity`) %>%
  kable(digits = 2, align = c(rep("l", 2), rep("r", ncol(.) - 2))) %>%
  kable_styling(font_size = 16) # %>%
  # collapse_rows(1:2)
```

# Primary analysis

## Table S20

```{r}
r1 <- lmer(spev_score ~ por_score 
           + (por_score | country/religion),
           # + (1 | country/religion),
           control = lmerControl(optimizer = "bobyqa"),
           data = d2 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r1)
```

```{r}
regtab_fun(r1, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1) %>% regtab_style_fun()
```


# Bayesian version

## Table S21

```{r}
# r1_bayes <- brm(spev_score ~ por_score
#                 + (por_score | country/religion),
#                 data = d2 %>% mutate_at(vars(ends_with("_score")), scale),
#                 control = list(adapt_delta = 0.999, max_treedepth = 12),
#                 seed = 1234, cores = 4, chains = 4)
# saveRDS(r1_bayes, "./models/r1_bayes.RDS")

r1_bayes <- readRDS("./models/r1_bayes.RDS")
```

```{r}
bayes_R2(r1_bayes)
```

```{r}
regtab_fun(r1_bayes, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_bayes) %>% regtab_style_fun()
```


# Country as fixed effect

## Table S22

```{r}
r2 <- lm(spev_score ~ por_score * country * religion,
         data = d2 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r2)
```

```{r}
regtab_fun(r2, std_beta = T, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```


# Other analyses

## Primary analysis, by country (Supplemental Information, p. 9)

```{r}
r1_us <- lmer(spev_score ~ por_score 
              + (1 | religion), 
              # + (por_score | religion), # singular
              control = lmerControl(optimizer = "bobyqa"),
              data = d2 %>% 
                filter(country == "US") %>%
                mutate_at(vars(ends_with("_score")), scale))

r1_gh <- lmer(spev_score ~ por_score 
              + (1 | religion),
              # + (por_score | religion), # singular
              control = lmerControl(optimizer = "bobyqa"),
              data = d2 %>% 
                filter(country == "Ghana") %>%
                mutate_at(vars(ends_with("_score")), scale))

r1_th <- lmer(spev_score ~ por_score 
              + (1 | religion),
              # + (por_score | religion), # singular
              control = lmerControl(optimizer = "bobyqa"),
              data = d2 %>% 
                filter(country == "Thailand") %>%
                mutate_at(vars(ends_with("_score")), scale))

r1_ch <- lmer(spev_score ~ por_score 
              + (1 | religion), # still singular, but using anyway
              # + (por_score | religion), # singular
              control = lmerControl(optimizer = "bobyqa"),
              data = d2 %>% 
                filter(country == "China") %>%
                mutate_at(vars(ends_with("_score")), scale))

r1_vt <- lmer(spev_score ~ por_score 
              + (1 | religion), # still singular, but using anyway
              # + (por_score | religion), # singular
              control = lmerControl(optimizer = "bobyqa"),
              data = d2 %>% 
                filter(country == "Vanuatu") %>%
                mutate_at(vars(ends_with("_score")), scale))
```

```{r}
bind_rows(regtab_fun(r1_us) %>% mutate(Country = "US"),
          regtab_fun(r1_gh) %>% mutate(Country = "Ghana"),
          regtab_fun(r1_th) %>% mutate(Country = "Thailand"),
          regtab_fun(r1_ch) %>% mutate(Country = "China"),
          regtab_fun(r1_vt) %>% mutate(Country = "Vanuatu")) %>%
  select(Country, everything()) %>%
  regtab_style_fun(row_emph = seq(2, 10, 2)) %>%
  collapse_rows(1)
```


## Primary analysis, evangelical charismatic Christians alone (Table S23)

```{r}
r3 <- lmer(spev_score ~ por_score 
           + (por_score | country),
           # + (1 | country),
           control = lmerControl(optimizer = "bobyqa"),
           data = d2 %>%
             filter(religion == "charismatic") %>%
             mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r3)
```

```{r}
regtab_fun(r3, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r3) %>% regtab_style_fun()
```



