---
title: "Study 4: Exploratory factor analyses"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    toc: true
    toc_float: true
---

In Study 4, college undergraduates completed a survey consisting of nine measures, including two indices of porosity, the Absorption scale, two indices of spiritual experience, two indices of more secular extraordinary experience, and two control measures.

This notebook contains exploratory factor analyses of item-wise data from this study.

```{r, message = F}
source("../scripts_general/dependencies.R")
source("../scripts_general/custom_funs.R")
source("../scripts_general/var_recode_contrast.R")
source("../scripts_general/data_load.R")
```

```{r}
require(readxl)
```

```{r}
d4_key <- read_excel("./data_by_question/Packet 7_CODED_March 18, 2019.xlsx", 
                     sheet = "Key") %>%
  rename(question = VARIABLE,
         question_text = QUESTION, 
         response_options = RESPONSES,
         coding = CODING) %>%
  mutate(question_text = gsub("[[:space:]]+", " ", question_text),
         question_text = gsub("’", "'", question_text),
         question_text = gsub("“", "'", question_text),
         question_text = gsub("”", "'", question_text),
         question_text = gsub("—", " - ", question_text),
         question_text = gsub("\\[ESP", "\\(ESP", question_text),
         question_text = gsub("psychic ability\\]", "psychic ability\\)", 
                              question_text),
         question_text = gsub(" \\[.*\\]", "", question_text),
         question_text = gsub("^[[:space:]]+", "", question_text))
```

```{r more custom funs}
nfact_fun <- function(df, which_rotate = "none") {
  
  res_par <- fa.parallel(df, plot = F)
  
  res_VSS <- VSS(df, n = 20, rotate = which_rotate, plot = F)
  
  res <- bind_rows(c(protocol = "Parallel analysis", 
                     nfact = res_par$nfact),
                   c(protocol = "Minimizing BIC", 
                     nfact = which.min(res_VSS$vss.stats$BIC)),
                   c(protocol = "Velicer's MAP",
                     nfact = which.min(res_VSS$map))) %>%
    mutate(nfact = as.numeric(nfact)) %>%
    arrange(nfact)
  
  return(res)
}

loadings_fun <- function(efa, key = d4_key) {
  res <- efa$loadings[] %>%
    data.frame() %>%
    rownames_to_column("question") %>%
    mutate(order = 1:nrow(.)) %>%
    gather(factor, loading, -c(question, order)) %>%
    left_join(key %>% select(question, question_text)) %>%
    mutate(scale = gsub("p7_", "", question),
           scale = gsub("_.*$", "", scale),
           scale_abbrev = factor(scale,
                                 levels = c("se", "dse", "por", "mm", "abs",
                                            "unev", "exsen", "hthk", "wob"),
                                 labels = c("SE", "DSE", "PS", "PV", "Abs.",
                                            "Hall.", "Para.", "NC", "SCM")),
           scale = factor(scale,
                          levels = c("se", "dse", "por", "mm", "abs",
                                     "unev", "exsen", "hthk", "wob"),
                          labels = c("Spiritual Events", 
                                     "Daily Spiritual Experiences",
                                     "Porosity Scale", "Porosity Vignettes",
                                     "Absorption", "Hallucinations", "Paranormal",
                                     "Need for Cognition", 
                                     "Sense of Control: Mastery")))
  
  return(res)
}

heatmap_fun <- function(df, wrap_width = 100, facet = F, legend = F, abbrev = T) {
  
  if (abbrev) {
    df <- df %>%
      mutate(scale = scale_abbrev,
             question_text = gsub("^.\\. ", "", question_text),
             question_text = gsub("^..\\. ", "", question_text),
             question_text = gsub("^.\\) ", "", question_text),
             question_text = gsub("^..\\) ", "", question_text))
  }

  if (!facet) {
    df <- df %>%
      unite(question_text, scale, question_text, sep = ": ")
  }
  
  plot <- ggplot(df,
                 aes(x = factor, 
                     y = reorder(str_wrap(question_text, wrap_width), desc(order)), 
                     fill = loading)) +
    geom_tile(color = "black", size = 0.1) +
    geom_text(aes(label = format(round(loading, 2), nsmall = 2)), size = 2) +
    scale_fill_viridis_c(guide = guide_colorbar(barwidth = 6, barheight = 0.5)) +
    scale_x_discrete(position = "top") +
    scale_y_discrete(position = "right") +
    theme_minimal() +
    theme(legend.position = "top") +
    labs(x = "Factor", y = "Question")
  
  if (facet) {
    plot <- plot + 
      facet_grid(rows = vars(scale), space = "free", scales = "free", switch = "y")
  }
  
  if (!legend) {
    plot <- plot + theme(legend.position = "none")
  }
  
  return(plot)
} 

topfact_fun <- function(df) {
  res <- df %>%
    group_by(question) %>%
    top_n(1, abs(loading)) %>%
    ungroup() %>%
    distinct(question, factor) %>%
    rename(topfact = factor)
  
  return(res)
}
```


# All items, standardized by site

```{r}
d4_items_all_std <- read_csv("./data_by_question/study4_byquestion.csv") %>%
  select(-X1, -ends_with("_cat"), -contains("_dem_"), 
         -contains("_total"), -contains("_check"),
         -ends_with("_physical"), # omit "physically" items from porosity vignettes
         -ends_with("_a"), -ends_with("_b"), -ends_with("_c")) %>%
  filter(p7_subj %in% d4$subject_id) %>%
  group_by(p7_ctry) %>%
  mutate_at(vars(-p7_ctry, -p7_subj), ~ scale(.)) %>%
  ungroup() %>%
  unite(ctry_subj, p7_ctry, p7_subj) %>%
  column_to_rownames("ctry_subj")
```

## Factor retention

```{r}
nfact_all_std <- nfact_fun(d4_items_all_std)
```

```{r}
nfact_all_std
```

## 5-factor solution

```{r}
efa_all_std_5 <- fa(d4_items_all_std, nfactors = 5, rotate = "varimax") %>% fa.sort()
colnames(efa_all_std_5$loadings) <- paste0("F", str_pad(1:5, width = 2, pad = "0"))
colnames(efa_all_std_5$Vaccounted) <- paste0("F", str_pad(1:5, width = 2, pad = "0"))
```

```{r}
efa_all_std_5_loadings <- loadings_fun(efa_all_std_5)
```

```{r}
efa_all_std_5$Vaccounted
```

```{r, fig.width = 4, fig.asp = 6}
heatmap_fun(efa_all_std_5_loadings)
```

```{r}
efa_all_std_5_topfact <- topfact_fun(efa_all_std_5_loadings)
```

```{r}
efa_all_std_5_topfact %>%
  left_join(efa_all_std_5_loadings %>% distinct(question, scale)) %>%
  count(topfact, scale) %>%
  spread(topfact, n)
```

```{r}
efa_all_std_5_topfact %>% count(topfact)
```

### Table S62. Factor loadings from of an exploratory factor analysis of item-wise data from all measures included in Study 4

_Note that the version of this table included in the Supplement was lightly edited in Microsoft Word._

```{r}
efa_all_std_5_loadings %>%
  select(scale, question_text, factor, loading, order) %>%
  mutate(factor = gsub("F0", "Factor ", factor),
         loading = format(round(loading, 2), nsmall = 2)) %>%
  spread(factor, loading) %>%
  arrange(order) %>%
  select(-order) %>%
  # mutate("Factor 1" = cell_spec(`Factor 1`, "html",
  #                               bold = c(rep(T, 35), 
  #                                        rep(F, nrow(.) - 35))),
  #        "Factor 2" = cell_spec(`Factor 2`, "html",
  #                               bold = c(rep(F, 35), 
  #                                        rep(T, 17), 
  #                                        rep(F, nrow(.) - (35 + 17)))),
  #        "Factor 3" = cell_spec(`Factor 3`, "html",
  #                               bold = c(rep(F, 35 + 17), 
  #                                        rep(T, 21),
  #                                        rep(F, nrow(.) - (35 + 17 + 21)))),
  #        "Factor 4" = cell_spec(`Factor 4`, "html",
  #                               bold = c(rep(F, 35 + 17 + 21), 
  #                                        rep(T, 45),
  #                                        rep(F, nrow(.) - (35 + 17 + 21 + 45)))),
  #        "Factor 5" = cell_spec(`Factor 5`, "html",
  #                               bold = c(rep(F, 35 + 17 + 21 + 45), 
  #                                        rep(T, 25)))) %>%
  kable(format = "html", escape = F) %>%
  kable_styling()
  
```






## 15-factor solution

```{r}
efa_all_std_15 <- fa(d4_items_all_std, nfactors = 15, rotate = "varimax") %>% fa.sort()
colnames(efa_all_std_15$loadings) <- paste0("F", str_pad(1:15, width = 2, pad = "0"))
colnames(efa_all_std_15$Vaccounted) <- paste0("F", str_pad(1:15, width = 2, pad = "0"))
```

```{r}
efa_all_std_15_loadings <- loadings_fun(efa_all_std_15)
```

```{r}
efa_all_std_15$Vaccounted
```

```{r, fig.width = 5, fig.asp = 5}
heatmap_fun(efa_all_std_15_loadings %>%
              mutate(question_text = ifelse(nchar(question_text) <= 80,
                                            question_text,
                                            paste0(substr(question_text, 1, 80), 
                                                   "..."))), 
            wrap_width = 80)
```

```{r}
efa_all_std_15_topfact <- topfact_fun(efa_all_std_15_loadings)
```

```{r}
efa_all_std_15_topfact %>%
  left_join(efa_all_std_15_loadings %>% distinct(question, scale)) %>%
  count(topfact, scale) %>%
  spread(topfact, n) %>%
  janitor::adorn_totals(where = "col")
```


# All items, standardized collapsing across sites

```{r}
d4_items_all <- read_csv("./data_by_question/study4_byquestion.csv") %>%
  select(-X1, -ends_with("_cat"), -contains("_dem_"), 
         -contains("_total"), -contains("_check"),
         -ends_with("_physical"), # omit "physically" items from porosity vignettes
         -ends_with("_a"), -ends_with("_b"), -ends_with("_c")) %>%
  filter(p7_subj %in% d4$subject_id) %>%
  unite(ctry_subj, p7_ctry, p7_subj) %>%
  column_to_rownames("ctry_subj") %>%
  mutate_all(~ scale(.))
```

## Factor retention

```{r}
nfact_all <- nfact_fun(d4_items_all)
```

```{r}
nfact_all
```

## 6-factor solution

```{r}
efa_all_6 <- fa(d4_items_all, nfactors = 6, rotate = "oblimin") %>% fa.sort()
colnames(efa_all_6$loadings) <- paste0("F", str_pad(1:6, width = 2, pad = "0"))
```

```{r}
efa_all_6_loadings <- loadings_fun(efa_all_6)
```

```{r, fig.width = 4, fig.asp = 6}
heatmap_fun(efa_all_6_loadings)
```
```{r}
efa_all_6_topfact <- topfact_fun(efa_all_6_loadings)
```

```{r}
efa_all_6_topfact %>%
  left_join(efa_all_6_loadings %>% distinct(question, scale)) %>%
  count(topfact, scale) %>%
  spread(topfact, n)
```

## 12-factor solution

```{r}
efa_all_12 <- fa(d4_items_all, nfactors = 12, rotate = "oblimin") %>% fa.sort()
colnames(efa_all_12$loadings) <- paste0("F", str_pad(1:12, width = 2, pad = "0"))
```

```{r}
efa_all_12_loadings <- loadings_fun(efa_all_12)
```

```{r, fig.width = 4, fig.asp = 6}
heatmap_fun(efa_all_12_loadings %>%
              mutate(question_text = ifelse(nchar(question_text) <= 100,
                                            question_text,
                                            paste0(substr(question_text, 1, 100), 
                                                   "..."))), 
            wrap_width = 60)
```
```{r}
efa_all_12_topfact <- topfact_fun(efa_all_12_loadings)
```

```{r}
efa_all_12_topfact %>%
  left_join(efa_all_12_loadings %>% distinct(question, scale)) %>%
  count(topfact, scale) %>%
  spread(topfact, n)
```


## 15-factor solution

```{r}
efa_all_15 <- fa(d4_items_all, nfactors = 15, rotate = "oblimin") %>% fa.sort()
colnames(efa_all_15$loadings) <- paste0("F", str_pad(1:15, width = 2, pad = "0"))
```

```{r}
efa_all_15_loadings <- loadings_fun(efa_all_15)
```

```{r, fig.width = 5, fig.asp = 5}
heatmap_fun(efa_all_15_loadings %>%
              mutate(question_text = ifelse(nchar(question_text) <= 80,
                                            question_text,
                                            paste0(substr(question_text, 1, 80), 
                                                   "..."))), 
            wrap_width = 80)
```

```{r}
efa_all_15_topfact <- topfact_fun(efa_all_15_loadings)
```

```{r}
efa_all_15_topfact %>%
  left_join(efa_all_15_loadings %>% distinct(question, scale)) %>%
  count(topfact, scale) %>%
  spread(topfact, n)
```

