---
title: "R Notebook"
output: html_notebook
---

# Standarizing and terciles within site

```{r}
d4_within_site <- d4 %>%
         group_by(country) %>%
         mutate_at(vars(ends_with("_score")),
                   ~ scale(.)) %>%
         mutate(por_level = factor(ntile(por_score, 3)),
                pv_level = factor(ntile(pv_score, 3)),
                abs_level = factor(ntile(abs_score, 3))) %>%
         ungroup() %>%
  mutate_at(vars(ends_with("_level")), ~ factor(., labels = c("low", "mid", "high")))
```

```{r}
cat("Porosity Scale terciles, number of participants by country")
d4_within_site %>%
  count(country, por_level) %>%
  spread(por_level, n)
```

```{r}
cat("Porosity Vignettes terciles, number of participants by country")
d4_within_site %>%
  count(country, pv_level) %>%
  spread(pv_level, n)
```

## Spiritual events

### Porosity Scale x Absorption

```{r, fig.width = 6, fig.asp = 0.3}
ggplot(d4_within_site,
       aes(x = abs_score, y = spev_score, color = por_level, fill = por_level)) +
  facet_grid(cols = vars(country)) +
  # geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", alpha = 0.1) +
  scale_color_viridis_d(aesthetics = c("color", "fill")) +
  labs(title = "Interactions, by site",
       subtitle = "All scores standardized within site\nTerciles calculated within site",
       x = "Absorption score",
       y = "Spiritual Events score",
       fill = "Porosity Scale Tercile",
       color = "Porosity Scale Tercile")
```

### Porosity Vignettes x Absorption

```{r, fig.width = 6, fig.asp = 0.3}
ggplot(d4_within_site,
       aes(x = abs_score, y = spev_score, color = pv_level, fill = pv_level)) +
  facet_grid(cols = vars(country)) +
  # geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", alpha = 0.1) +
  scale_color_viridis_d(aesthetics = c("color", "fill")) +
  labs(title = "Interactions, by site",
       subtitle = "All scores standardized within site\nTerciles calculated within site",
       x = "Absorption score",
       y = "Spiritual Events score",
       fill = "Porosity Vignettes Tercile",
       color = "Porosity Vignettes Tercile")
```


## Daily Spiritual Experiences

### Porosity Scale x Absorption

```{r, fig.width = 6, fig.asp = 0.3}
ggplot(d4_within_site,
       aes(x = abs_score, y = dse_score, color = por_level, fill = por_level)) +
  facet_grid(cols = vars(country)) +
  # geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", alpha = 0.1) +
  scale_color_viridis_d(aesthetics = c("color", "fill")) +
  labs(title = "Interactions, by site",
       subtitle = "All scores standardized within site\nTerciles calculated within site",
       x = "Absorption score",
       y = "DSE score",
       fill = "Porosity Scale Tercile",
       color = "Porosity Scale Tercile")
```

### Porosity Vignettes x Absorption

```{r, fig.width = 6, fig.asp = 0.3}
ggplot(d4_within_site,
       aes(x = abs_score, y = dse_score, color = pv_level, fill = pv_level)) +
  facet_grid(cols = vars(country)) +
  # geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", alpha = 0.1) +
  scale_color_viridis_d(aesthetics = c("color", "fill")) +
  labs(title = "Interactions, by site",
       subtitle = "All scores standardized within site\nTerciles calculated within site",
       x = "Absorption score",
       y = "DSE score",
       fill = "Porosity Vignettes Tercile",
       color = "Porosity Vignettes Tercile")
```



# Standarizing and terciles across sites

```{r}
d4_across_sites <- d4 %>%
         mutate_at(vars(ends_with("_score")),
                   ~ scale(.)) %>%
         mutate(por_level = factor(ntile(por_score, 3)),
                pv_level = factor(ntile(pv_score, 3)),
                abs_level = factor(ntile(abs_score, 3))) %>%
  mutate_at(vars(ends_with("_level")), ~ factor(., labels = c("low", "mid", "high")))
```

```{r}
cat("Porosity Scale terciles, number of participants by country")
d4_across_sites %>%
  count(country, por_level) %>%
  spread(por_level, n)
```

```{r}
cat("Porosity Vignettes terciles, number of participants by country")
d4_across_sites %>%
  count(country, pv_level) %>%
  spread(pv_level, n)
```

## Spiritual events

### Porosity Scale x Absorption

```{r, fig.width = 6, fig.asp = 0.3}
ggplot(d4_across_sites,
       aes(x = abs_score, y = spev_score, color = por_level, fill = por_level)) +
  facet_grid(cols = vars(country)) +
  # geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", alpha = 0.1) +
  scale_color_viridis_d(aesthetics = c("color", "fill")) +
  labs(title = "Interactions, by site",
       subtitle = "All scores standardized within site\nTerciles calculated within site",
       x = "Absorption score",
       y = "Spiritual Events score",
       fill = "Porosity Scale Tercile",
       color = "Porosity Scale Tercile")
```

### Porosity Vignettes x Absorption

```{r, fig.width = 6, fig.asp = 0.3}
ggplot(d4_across_sites,
       aes(x = abs_score, y = spev_score, color = pv_level, fill = pv_level)) +
  facet_grid(cols = vars(country)) +
  # geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", alpha = 0.1) +
  scale_color_viridis_d(aesthetics = c("color", "fill")) +
  labs(title = "Interactions, by site",
       subtitle = "All scores standardized within site\nTerciles calculated within site",
       x = "Absorption score",
       y = "Spiritual Events score",
       fill = "Porosity Vignettes Tercile",
       color = "Porosity Vignettes Tercile")
```


## Daily Spiritual Experiences

### Porosity Scale x Absorption

```{r, fig.width = 6, fig.asp = 0.3}
ggplot(d4_across_sites,
       aes(x = abs_score, y = dse_score, color = por_level, fill = por_level)) +
  facet_grid(cols = vars(country)) +
  # geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", alpha = 0.1) +
  scale_color_viridis_d(aesthetics = c("color", "fill")) +
  labs(title = "Interactions, by site",
       subtitle = "All scores standardized within site\nTerciles calculated within site",
       x = "Absorption score",
       y = "DSE score",
       fill = "Porosity Scale Tercile",
       color = "Porosity Scale Tercile")
```

### Porosity Vignettes x Absorption

```{r, fig.width = 6, fig.asp = 0.3}
ggplot(d4_across_sites,
       aes(x = abs_score, y = dse_score, color = pv_level, fill = pv_level)) +
  facet_grid(cols = vars(country)) +
  # geom_point(alpha = 0.2) +
  geom_smooth(method = "lm", alpha = 0.1) +
  scale_color_viridis_d(aesthetics = c("color", "fill")) +
  labs(title = "Interactions, by site",
       subtitle = "All scores standardized within site\nTerciles calculated within site",
       x = "Absorption score",
       y = "DSE score",
       fill = "Porosity Vignettes Tercile",
       color = "Porosity Vignettes Tercile")
```

