---
title: "Study 1"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    toc: true
    toc_float: true
---

In Study 1, adults with strong religious commitments and faith practices were interviewed in depth about their spiritual experiences and their understanding of the mind by experienced ethnographers. These interviews yielded one measure of porosity (“Porosity Vignettes”), one measure of absorption (the Absorption scale), and one measure of spiritual experience (“Spiritual Events” scale).

This notebook contains all of the analyses for Study 1 (revised July 2020).

```{r, message = F}
source("../scripts_general/dependencies.R")
source("../scripts_general/custom_funs.R")
source("../scripts_general/var_recode_contrast.R")
source("../scripts_general/data_load.R")
```


# Demographics (Table S14)

```{r}
d1_demo <- d1 %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age),
         subject_hs = ifelse(grepl("yes", tolower(subject_hs)), 1, 0))
```

```{r}
d1_demo %>%
  filter(!is.na(country), !is.na(site), !is.na(religion)) %>%
  mutate(site = factor(site, levels = c("urban", "rural"))) %>%
  group_by(country, site, religion) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_hs = mean(subject_hs, na.rm = T),
            percent_special = mean(subject_specialrole, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, Site = site, Religion = religion,
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% attended high school` = percent_hs,
         `% serving a 'special role'` = percent_special) %>%
  kable(digits = 2, align = c(rep("l", 3), rep("r", 4))) %>%
  kable_styling(font_size = 16) # %>%
# collapse_rows(1:2)
```


# Regression analyses (Tables S18-S23)

## Setup

```{r}
# dataframe with variable names optimized for stargazer tables
d1_fortab <- d1 %>%
  mutate_at(vars(ends_with("_score"), subject_age), scale) %>%
  mutate(subject_hs = case_when(is.na(subject_hs) ~ NA_character_,
                                grepl("yes", tolower(subject_hs)) ~ "yes",
                                TRUE ~ "no"),
         subject_hs = factor(subject_hs, 
                             levels = c("no", "yes")),
         subject_gender = factor(subject_gender, 
                                 levels = c("Female", "Male"))) %>%
  rename("Spiritual Events" = "spev_score",
         "Spiritual Events, recoded" = "spev_recoded_score",
         "Porosity Vignettes" = "pv_score",
         "Absorption" = "abs_score",
         "Country" = "country",
         "Site" = "site",
         "Religion" = "religion",
         "Gender" = "subject_gender",
         "Age" = "subject_age",
         "Education" = "subject_hs")
```

```{r}
# set contrasts
contrasts(d1_fortab$Country) <- cbind(": Gh." = c(-1, 1, 0, 0, 0),
                                      ": Th." = c(-1, 0, 1, 0, 0),
                                      ": Ch." = c(-1, 0, 0, 1, 0),
                                      ": Va." = c(-1, 0, 0, 0, 1))
contrasts(d1_fortab$Site) <- cbind(": rural" = c(-1, 1))
contrasts(d1_fortab$Religion) <- cbind(": CC" = c(1, -1))
contrasts(d1_fortab$Education) <- cbind(": at least HS" = c(-1, 1))
contrasts(d1_fortab$Gender) <- cbind(": male" = c(-1, 1))
```

```{r}
# show contrasts
cat("Country\n"); contrasts(d1_fortab$Country)
cat("Site\n"); contrasts(d1_fortab$Site)
cat("Religion\n"); contrasts(d1_fortab$Religion)
cat("Education\n"); contrasts(d1_fortab$Education)
cat("Gender\n"); contrasts(d1_fortab$Gender)
```

## Group differences

### Table S18. Spiritual Events: group differences

```{r}
r01_spev <- lm(`Spiritual Events` ~ Country,
               data = d1_fortab)
r02_spev <- lm(`Spiritual Events` ~ Country * Site * Religion, 
               data = d1_fortab)
r03_spev <- lm(`Spiritual Events` ~ Country * Site * Religion +
                 Gender + Age + Education,
               data = d1_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r01_spev)
summary(r02_spev)
summary(r03_spev)
```

```{r}
r01_spev_recoded <- lm(`Spiritual Events, recoded` ~ Country,
                       data = d1_fortab)
r02_spev_recoded <- lm(`Spiritual Events, recoded` ~ Country * Site * Religion, 
                       data = d1_fortab)
r03_spev_recoded <- lm(`Spiritual Events, recoded` ~ Country * Site * Religion +
                         Gender + Age + Education,
                       data = d1_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r01_spev_recoded)
summary(r02_spev_recoded)
summary(r03_spev_recoded)
```

```{r, results = "hide"}
table_s18 <- stargazer(r01_spev, r02_spev, r03_spev, 
                       r01_spev_recoded, r02_spev_recoded, r03_spev_recoded, 
                       type = "html",
                       ci = T,
                       report = c("vcsp"),
                       digits = 2,
                       digits.extra = 1000,
                       omit.table.layout = "n",
                       # dep.var.labels.include = F,
                       dep.var.caption = "",
                       single.row = T)

cat(sub_interact_fun(table_s18), 
    file = "./stargazer_tables/table_s18.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s18.html")
```


### Table S19. Porosity Vignettes and Absorption: group differences

```{r}
r01_pv <- lm(`Porosity Vignettes` ~ Country,
             data = d1_fortab)
r02_pv <- lm(`Porosity Vignettes` ~ Country * Site * Religion, 
             data = d1_fortab)
r03_pv <- lm(`Porosity Vignettes` ~ Country * Site * Religion +
               Gender + Age + Education,
             data = d1_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r01_pv)
summary(r02_pv)
summary(r03_pv)
```

```{r}
r01_abs <- lm(`Absorption` ~ Country,
              data = d1_fortab)
r02_abs <- lm(`Absorption` ~ Country * Site * Religion, 
              data = d1_fortab)
r03_abs <- lm(`Absorption` ~ Country * Site * Religion +
                Gender + Age + Education,
              data = d1_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r01_abs)
summary(r02_abs)
summary(r03_abs)
```

```{r, results = "hide"}
table_s19 <- stargazer(r01_pv, r02_pv, r03_pv, 
                       r01_abs, r02_abs, r03_abs, 
                       type = "html",
                       ci = T,
                       report = c("vcsp"),
                       digits = 2,
                       digits.extra = 1000,
                       omit.table.layout = "n",
                       # dep.var.labels.include = F,
                       dep.var.caption = "",
                       single.row = T)

cat(sub_interact_fun(table_s19), 
    file = "./stargazer_tables/table_s19.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s19.html")
```


## Relationships

### Table S20. Study 1, Spiritual Events: relationships with Porosity Vignettes and Absorption (sample as fixed effect)

```{r}
r04_spev <- lm(`Spiritual Events` ~ `Porosity Vignettes`,
               data = d1_fortab)

r05_spev <- lm(`Spiritual Events` ~ Absorption,
               data = d1_fortab)

r06_spev <- lm(`Spiritual Events` ~ `Porosity Vignettes` * Absorption,
               data = d1_fortab)

r07_spev <- lm(`Spiritual Events` ~ Country * Site * Religion 
               + `Porosity Vignettes` + Country:`Porosity Vignettes`,
               data = d1_fortab)

r08_spev <- lm(`Spiritual Events` ~ Country * Site * Religion 
               + Absorption + Country:Absorption,
               data = d1_fortab)

r09_spev <- lm(`Spiritual Events` ~ Country * Site * Religion 
               + `Porosity Vignettes` + Country:`Porosity Vignettes`
               + Absorption + Country:Absorption
               + `Porosity Vignettes`:Absorption 
               + Country:`Porosity Vignettes`:Absorption,
               data = d1_fortab)

r10_spev <- lm(`Spiritual Events` ~ Country * Site * Religion 
               + `Porosity Vignettes` + Country:`Porosity Vignettes`
               + Absorption + Country:Absorption
               + `Porosity Vignettes`:Absorption
               + Country:`Porosity Vignettes`:Absorption
               + Gender + Age + Education,
               data = d1_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r04_spev)
summary(r05_spev)
summary(r06_spev)
summary(r07_spev)
summary(r08_spev)
summary(r09_spev)
summary(r10_spev)
```

```{r, results = "hide"}
table_s20 <- stargazer(r04_spev, r05_spev, r06_spev, 
                       r07_spev, r08_spev, r09_spev, r10_spev,
                       type = "html",
                       ci = T,
                       report = c("vcsp"),
                       digits = 2,
                       digits.extra = 1000,
                       omit.table.layout = "n",
                       order = c("^`Porosity Vignettes`$",
                                 "^Absorption$",
                                 "^`Porosity Vignettes`:Absorption$"),
                       # dep.var.labels.include = F,
                       dep.var.caption = "",
                       single.row = T)

cat(sub_interact_fun(table_s20), 
    file = "./stargazer_tables/table_s20.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s20.html")
```

### Table S21. Study 1, Spiritual Events: relationships with Porosity Vignettes and Absorption (sample as random effect)

```{r}
r11_spev <- lmer(`Spiritual Events` ~ 1 
                 + (1 | Country/Site/Religion),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d1_fortab)

r12_spev <- lmer(`Spiritual Events` ~ `Porosity Vignettes` 
                 # + (1 + `Porosity Vignettes` | Country/Site/Religion),
                 + (1 | Country/Site/Religion),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d1_fortab)

r13_spev <- lmer(`Spiritual Events` ~ Absorption
                 # + (1 + Absorption | Country/Site/Religion),
                 + (1 | Country/Site/Religion),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d1_fortab)

r14_spev <- lmer(`Spiritual Events` ~ `Porosity Vignettes` * Absorption 
                 # + (1 + `Porosity Vignettes` * Absorption | Country/Site/Religion),
                 # + (1 + `Porosity Vignettes` + Absorption | Country/Site/Religion),
                 + (1 | Country/Site/Religion),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d1_fortab)

r15_spev <- lmer(`Spiritual Events` ~ `Porosity Vignettes` * Absorption
                 + Gender + Age + Education
                 # + (1 + `Porosity Vignettes` * Absorption | Country/Site/Religion),
                 # + (1 + `Porosity Vignettes` + Absorption | Country/Site/Religion),
                 + (1 | Country/Site/Religion),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d1_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r11_spev)
summary(r12_spev)
summary(r13_spev)
summary(r14_spev)
summary(r15_spev)
```

```{r, include=F}
table_s21 <- stargazer(#r04_spev, r05_spev, r06_spev, 
  r11_spev, r12_spev, r13_spev, r14_spev, r15_spev,
  type = "html",
  ci = T,
  report = c("vcsp"),
  digits = 2,
  digits.extra = 1000,
  omit.table.layout = "n",
  order = c("^`Porosity Vignettes`$",
            "^Absorption$",
            "^`Porosity Vignettes`:Absorption$"),
  # dep.var.labels.include = F,
  dep.var.caption = "",
  single.row = T)

cat(sub_interact_fun(table_s21), 
    file = "./stargazer_tables/table_s21.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s21.html")
```

```{r}
rsq_table_fun(list(r11_spev, r12_spev, r13_spev, r14_spev, r15_spev))
```

### Table S22. Study 1, Spiritual Events, recoded: relationships with Porosity Vignettes and Absorption (sample as fixed effect)

```{r}
r04_spev_recoded <- lm(`Spiritual Events, recoded` ~ `Porosity Vignettes`,
                       data = d1_fortab)

r05_spev_recoded <- lm(`Spiritual Events, recoded` ~ Absorption,
                       data = d1_fortab)

r06_spev_recoded <- lm(`Spiritual Events, recoded` ~ `Porosity Vignettes` * Absorption,
                       data = d1_fortab)

r07_spev_recoded <- lm(`Spiritual Events, recoded` ~ Country * Site * Religion 
                       + `Porosity Vignettes` + Country:`Porosity Vignettes`,
                       data = d1_fortab)

r08_spev_recoded <- lm(`Spiritual Events, recoded` ~ Country * Site * Religion 
                       + Absorption + Country:Absorption,
                       data = d1_fortab)

r09_spev_recoded <- lm(`Spiritual Events, recoded` ~ Country * Site * Religion 
                       + `Porosity Vignettes` + Country:`Porosity Vignettes`
                       + Absorption + Country:Absorption
                       + `Porosity Vignettes`:Absorption 
                       + Country:`Porosity Vignettes`:Absorption,
                       data = d1_fortab)

r10_spev_recoded <- lm(`Spiritual Events, recoded` ~ Country * Site * Religion 
                       + `Porosity Vignettes` + Country:`Porosity Vignettes`
                       + Absorption + Country:Absorption
                       + `Porosity Vignettes`:Absorption
                       + Country:`Porosity Vignettes`:Absorption
                       + Gender + Age + Education,
                       data = d1_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r04_spev_recoded)
summary(r05_spev_recoded)
summary(r06_spev_recoded)
summary(r07_spev_recoded)
summary(r08_spev_recoded)
summary(r09_spev_recoded)
summary(r10_spev_recoded)
```

```{r, results = "hide"}
table_s22 <- stargazer(r04_spev_recoded, r05_spev_recoded, r06_spev_recoded, 
                       r07_spev_recoded, r08_spev_recoded, r09_spev_recoded, r10_spev_recoded,
                       type = "html",
                       ci = T,
                       report = c("vcsp"),
                       digits = 2,
                       digits.extra = 1000,
                       omit.table.layout = "n",
                       order = c("^`Porosity Vignettes`$",
                                 "^Absorption$",
                                 "^`Porosity Vignettes`:Absorption$"),
                       # dep.var.labels.include = F,
                       dep.var.caption = "",
                       single.row = T)

cat(sub_interact_fun(table_s22), 
    file = "./stargazer_tables/table_s22.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s22.html")
```

### Table S23. Study 1, Spiritual Events, recoded: relationships with Porosity Vignettes and Absorption (sample as random effect)

```{r}
r11_spev_recoded <- lmer(`Spiritual Events, recoded` ~ 1 
                         + (1 | Country/Site/Religion),
                         control = lmerControl(optimizer = "bobyqa"),
                         data = d1_fortab)

r12_spev_recoded <- lmer(`Spiritual Events, recoded` ~ `Porosity Vignettes` 
                         # + (1 + `Porosity Vignettes` | Country/Site/Religion),
                         + (1 | Country/Site/Religion),
                         control = lmerControl(optimizer = "bobyqa"),
                         data = d1_fortab)

r13_spev_recoded <- lmer(`Spiritual Events, recoded` ~ Absorption
                         # + (1 + Absorption | Country/Site/Religion),
                         + (1 | Country/Site/Religion),
                         control = lmerControl(optimizer = "bobyqa"),
                         data = d1_fortab)

r14_spev_recoded <- lmer(`Spiritual Events, recoded` ~ `Porosity Vignettes` * Absorption 
                         # + (1 + `Porosity Vignettes` * Absorption | Country/Site/Religion),
                         # + (1 + `Porosity Vignettes` + Absorption | Country/Site/Religion),
                         + (1 | Country/Site/Religion),
                         control = lmerControl(optimizer = "bobyqa"),
                         data = d1_fortab)

r15_spev_recoded <- lmer(`Spiritual Events, recoded` ~ `Porosity Vignettes` * Absorption
                         + Gender + Age + Education
                         # + (1 + `Porosity Vignettes` * Absorption | Country/Site/Religion),
                         # + (1 + `Porosity Vignettes` + Absorption | Country/Site/Religion),
                         + (1 | Country/Site/Religion),
                         control = lmerControl(optimizer = "bobyqa"),
                         data = d1_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r11_spev_recoded)
summary(r12_spev_recoded)
summary(r13_spev_recoded)
summary(r14_spev_recoded)
summary(r15_spev_recoded)
```

```{r, include=F}
table_s23 <- stargazer(#r04_spev_recoded, r05_spev_recoded, r06_spev_recoded, 
  r11_spev_recoded, r12_spev_recoded, r13_spev_recoded, 
  r14_spev_recoded, r15_spev_recoded,
  type = "html",
  ci = T,
  report = c("vcsp"),
  digits = 2,
  digits.extra = 1000,
  omit.table.layout = "n",
  order = c("^`Porosity Vignettes`$",
            "^Absorption$",
            "^`Porosity Vignettes`:Absorption$"),
  # dep.var.labels.include = F,
  dep.var.caption = "",
  single.row = T)

cat(sub_interact_fun(table_s23), 
    file = "./stargazer_tables/table_s23.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s23.html")
```

```{r}
rsq_table_fun(list(r11_spev_recoded, r12_spev_recoded, r13_spev_recoded, 
                   r14_spev_recoded, r15_spev_recoded))
```


# Other analyses

## Simple correlations (Supplemental Information, p. 6)

```{r}
d1 %>% 
  mutate_at(vars(ends_with("_score")), scale) %>%
  select(pv_score, abs_score, spev_score) %>% 
  cor(use = "pairwise.complete")
```

```{r}
cor.test(scale(d1$pv_score), scale(d1$spev_score)) # standardizing unnecessary
```

```{r}
cor.test(scale(d1$abs_score), scale(d1$spev_score)) # standardizing unnecessary
```

```{r}
cor.test(scale(d1$pv_score), scale(d1$abs_score)) # standardizing unnecessary
```

