---
title: "Study 3"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    theme: flatly
    toc: true
    toc_float: true
---

In Study 3, college undergraduates completed a survey consisting of one measure of absorption (the Absorption scale) and two measures of spiritual experience (a “Spiritual Events” inventory based on Studies 1 and 2; and a modified version of the Daily Spiritual Experiences scale). 

This notebook contains all of the analyses for Study 3.

```{r, message = F}
source("../scripts_general/dependencies.R")
source("../scripts_general/custom_funs.R")
source("../scripts_general/var_recode_contrast.R")
source("../scripts_general/data_load.R")
```

```{r}
# show contrasts
contrasts(d3$country)
```

# Demographics

## Table S19

```{r}
d3_demo <- d3 %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age),
         subject_religion = case_when(
           subject_religion %in% 
             c("christian", "(seventh day adventist) youth", "a.o.g.", "anglican",
               "anglicanism", "aog", "aog assemblies of god", 
               "agos, assemblies of god", "assemblies of god",
               "c.m.c presbyterian", "christian - ame (google it!)",
               "christian: anglican", "christian: catholic", 
               "christian: non specific", "christian: non-specific",
               "christian: protestant mainline", "christianity",
               "christianity: non specific", "church of christ",
               "coptic orthodox christian",
               "family worship ark healing ministry",
               "kingdom citizenship of god", "living water", "ntm",
               "pentecostal", "presbyterian", "presbyterian (illegible)",
               "protestant", "s.d.a.", "sda", "sda (seventh day adventist)",
               "seven day adventist", "seventh day adventist", 
               "seventh day adventist church", "sunday keeper",
               "word christian fellowship") ~ "Christian",
           subject_religion %in% 
             c("buddhist", "dge-lugs-pa (buddhist sect)", "sanqi buddhism",
               "some values of buddhism", "buddha temple", "buddha temples",
               "buddha temples & ancestral hall", "buddhist temples") ~ "Buddhist",
           # subject_religion %in% 
           #   c("Family - Orthodox Jew / Jewish",
           #     "Judaism", "Orthodox Jewish") ~ "Jewish",
           subject_religion %in%
             c("muslim") ~ "Muslim",
           # subject_religion %in% 
           #   c("Hinduism") ~ "Hindu",
           grepl("agnost", tolower(subject_religion)) |
             grepl("atheis", tolower(subject_religion)) |
             grepl("don't", tolower(subject_religion)) |
             grepl("none", tolower(subject_religion)) |
             tolower(subject_religion) %in% 
             c("n/a", "no", "no religion", "not really") ~ "Agnostic/Atheist",
           subject_religion %in% c("missing data", "mdata", "NA") |
             is.na(subject_religion) ~ "Missing data",
           TRUE ~ "Other"),
         agnostic_atheist = (subject_religion == "Agnostic/Atheist"),
           buddhist = (subject_religion == "Buddhist"),
           christian = (subject_religion == "Christian"),
           muslim = (subject_religion == "Muslim"),
           other = (subject_religion == "Other"),
         missing = (subject_religion == "Missing data"))
```

```{r}
d3_demo %>%
  group_by(country) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_affr = mean(subject_afford, na.rm = T),
            mean_ses = mean(subject_ses, na.rm = T),
            mean_religiosity = mean(subject_religiosity, na.rm = T),
            percent_christian = mean(christian, na.rm = T),
            percent_agnostic_atheist = mean(agnostic_atheist, na.rm = T),
            percent_buddhist = mean(buddhist, na.rm = T),
            percent_muslim = mean(muslim, na.rm = T),
            percent_other = mean(other, na.rm = T),
            percent_missing = mean(missing, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, 
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% can afford` = percent_affr,
         `% Christian` = percent_christian, 
         `% Agnostic/Atheist` = percent_agnostic_atheist, 
         `% Buddhist` = percent_buddhist, 
         `% Muslim` = percent_muslim, 
         `% Other` = percent_other,
         `[% Missing data]` = percent_missing,
         `Mean SES` = mean_ses, `Mean religiosity` = mean_religiosity) %>%
  mutate(Country = factor(Country, levels = levels_country)) %>%
  arrange(Country) %>%
  select(Country, n, `Age range`, `Mean age`, `% male`, `% female`,
         `Mean religiosity`,
         `% Christian`, `% Buddhist`, `% Muslim`, `% Other`, `% Agnostic/Atheist`,
         `[% Missing data]`,
         `% can afford`, `Mean SES`) %>%
  kable(digits = 2, align = c(rep("l", 2), rep("r", ncol(.) - 2))) %>%
  kable_styling(font_size = 16) # %>%
# collapse_rows(1:2)
```

# Primary analyses

## Table S25 (Spiritual Events)

```{r}
r1_spev <- lmer(spev_score ~ abs_score 
                # + (abs_score | country), # singular
                + (abs_score || country),
                # + (1 | country),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r1_spev)
```

```{r}
regtab_fun(r1_spev) %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_spev) %>% regtab_style_fun()
```

## Table S26 (Daily Spiritual Experiences)

```{r}
r1_dse <- lmer(dse_score ~ abs_score 
               # + (abs_score | country), # singular
               + (abs_score || country),
               # + (1 | country),
               control = lmerControl(optimizer = "bobyqa"),
               data = d3 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r1_dse)
```

```{r}
regtab_fun(r1_dse) %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_dse) %>% regtab_style_fun()
```


# Bayesian versions

## Table S27 (Spiritual Events)

```{r}
# r1_spev_bayes <- brm(spev_score ~ abs_score
#                      + (abs_score || country),
#                      data = d3 %>% mutate_at(vars(ends_with("_score")), scale),
#                      control = list(adapt_delta = 0.999, max_treedepth = 12),
#                      seed = 1234, cores = 4, chains = 4)
# saveRDS(r1_spev_bayes, "./models/r1_spev_bayes.RDS")

r1_spev_bayes <- readRDS("./models/r1_spev_bayes.RDS")
```

```{r}
bayes_R2(r1_spev_bayes)
```

```{r}
regtab_fun(r1_spev_bayes, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_spev_bayes) %>% regtab_style_fun()
```

## Table S28 (Daily Spiritual Experiences)

```{r}
# r1_dse_bayes <- brm(dse_score ~ abs_score
#                      + (abs_score || country),
#                      data = d3 %>% mutate_at(vars(ends_with("_score")), scale),
#                      control = list(adapt_delta = 0.999, max_treedepth = 12),
#                      seed = 1234, cores = 4, chains = 4)
# saveRDS(r1_dse_bayes, "./models/r1_dse_bayes.RDS")

r1_dse_bayes <- readRDS("./models/r1_dse_bayes.RDS")
```

```{r}
bayes_R2(r1_dse_bayes)
```

```{r}
regtab_fun(r1_dse_bayes, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_dse_bayes) %>% regtab_style_fun()
```


# Country as fixed effect

## Table S29 (Spiritual Events)

```{r}
r2_spev <- lm(spev_score ~ abs_score * country,
              data = d3 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r2_spev)
```

```{r}
regtab_fun(r2_spev, std_beta = T, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```

## Table S30 (Daily Spiritual Experiences)

```{r}
r2_dse <- lm(dse_score ~ abs_score * country,
             data = d3 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r2_dse)
```

```{r}
regtab_fun(r2_dse, std_beta = T, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```


# Other analyses

## Primary analyses, by country (Supplemental Information, p. 12)

### Spiritual Events

```{r}
r1_spev_us <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "US") %>%
                   mutate_at(vars(ends_with("_score")), scale))

r1_spev_gh <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "Ghana") %>%
                   mutate_at(vars(ends_with("_score")), scale))

r1_spev_th <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "Thailand") %>%
                   mutate_at(vars(ends_with("_score")), scale))

r1_spev_ch <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "China") %>%
                   mutate_at(vars(ends_with("_score")), scale))

r1_spev_vt <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "Vanuatu") %>%
                   mutate_at(vars(ends_with("_score")), scale))
```

```{r}
bind_rows(regtab_fun(r1_spev_us) %>% mutate(Country = "US"),
          regtab_fun(r1_spev_gh) %>% mutate(Country = "Ghana"),
          regtab_fun(r1_spev_th) %>% mutate(Country = "Thailand"),
          regtab_fun(r1_spev_ch) %>% mutate(Country = "China"),
          regtab_fun(r1_spev_vt) %>% mutate(Country = "Vanuatu")) %>%
  select(Country, everything()) %>%
  regtab_style_fun(row_emph = seq(2, 10, 2)) %>%
  collapse_rows(1)
```

### Daily Spiritual Experiences

```{r}
r1_dse_us <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "US") %>%
                  mutate_at(vars(ends_with("_score")), scale))

r1_dse_gh <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "Ghana") %>%
                  mutate_at(vars(ends_with("_score")), scale))

r1_dse_th <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "Thailand") %>%
                  mutate_at(vars(ends_with("_score")), scale))

r1_dse_ch <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "China") %>%
                  mutate_at(vars(ends_with("_score")), scale))

r1_dse_vt <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "Vanuatu") %>%
                  mutate_at(vars(ends_with("_score")), scale))
```

```{r}
bind_rows(regtab_fun(r1_dse_us) %>% mutate(Country = "US"),
          regtab_fun(r1_dse_gh) %>% mutate(Country = "Ghana"),
          regtab_fun(r1_dse_th) %>% mutate(Country = "Thailand"),
          regtab_fun(r1_dse_ch) %>% mutate(Country = "China"),
          regtab_fun(r1_dse_vt) %>% mutate(Country = "Vanuatu")) %>%
  select(Country, everything()) %>%
  regtab_style_fun(row_emph = seq(2, 10, 2)) %>%
  collapse_rows(1)
```

