---
title: "Study 3"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    theme: flatly
    toc: true
    toc_float: true
---

In Study 3, college undergraduates completed a survey consisting of one measure of absorption (the Absorption scale) and two measures of spiritual experience (a “Spiritual Events” inventory based on Studies 1 and 2; and a modified version of the Daily Spiritual Experiences scale). 

This notebook contains all of the analyses for Study 3.

```{r, message = F}
source("../scripts_general/dependencies.R")
source("../scripts_general/custom_funs.R")
source("../scripts_general/var_recode_contrast.R")
source("../scripts_general/data_load.R")
```

```{r}
# show contrasts
contrasts(d3$country)
```

# Demographics

## Table S19

```{r}
d3_demo <- d3 %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age))
```

```{r}
d3_demo %>%
  group_by(country) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_affr = mean(subject_afford, na.rm = T),
            mean_ses = mean(subject_ses, na.rm = T),
            mean_howr = mean(subject_religiosity, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, 
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% can afford` = percent_affr,
         `Mean SES` = mean_ses, `Mean religiosity` = mean_howr) %>%
  mutate(Country = factor(Country, levels = levels_country)) %>%
  arrange(Country) %>%
  select(Country, n, `Age range`, `Mean age`, `% male`, `% female`,
         `% can afford`, `Mean SES`, `Mean religiosity`) %>%
  kable(digits = 2, align = c(rep("l", 2), rep("r", ncol(.) - 2))) %>%
  kable_styling(font_size = 16) # %>%
# collapse_rows(1:2)
```

# Primary analyses

## Table S25 (Spiritual Events)

```{r}
r1_spev <- lmer(spev_score ~ abs_score 
                # + (abs_score | country), # singular
                + (abs_score || country),
                # + (1 | country),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r1_spev)
```

```{r}
regtab_fun(r1_spev) %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_spev) %>% regtab_style_fun()
```

## Table S26 (Daily Spiritual Experiences)

```{r}
r1_dse <- lmer(dse_score ~ abs_score 
               # + (abs_score | country), # singular
               + (abs_score || country),
               # + (1 | country),
               control = lmerControl(optimizer = "bobyqa"),
               data = d3 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r1_dse)
```

```{r}
regtab_fun(r1_dse) %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_dse) %>% regtab_style_fun()
```


# Bayesian versions

## Table S27 (Spiritual Events)

```{r}
# r1_spev_bayes <- brm(spev_score ~ abs_score
#                      + (abs_score || country),
#                      data = d3 %>% mutate_at(vars(ends_with("_score")), scale),
#                      control = list(adapt_delta = 0.999, max_treedepth = 12),
#                      seed = 1234, cores = 4, chains = 4)
# saveRDS(r1_spev_bayes, "./models/r1_spev_bayes.RDS")

r1_spev_bayes <- readRDS("./models/r1_spev_bayes.RDS")
```

```{r}
bayes_R2(r1_spev_bayes)
```

```{r}
regtab_fun(r1_spev_bayes, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_spev_bayes) %>% regtab_style_fun()
```

## Table S28 (Daily Spiritual Experiences)

```{r}
# r1_dse_bayes <- brm(dse_score ~ abs_score
#                      + (abs_score || country),
#                      data = d3 %>% mutate_at(vars(ends_with("_score")), scale),
#                      control = list(adapt_delta = 0.999, max_treedepth = 12),
#                      seed = 1234, cores = 4, chains = 4)
# saveRDS(r1_dse_bayes, "./models/r1_dse_bayes.RDS")

r1_dse_bayes <- readRDS("./models/r1_dse_bayes.RDS")
```

```{r}
bayes_R2(r1_dse_bayes)
```

```{r}
regtab_fun(r1_dse_bayes, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```

```{r}
regtab_ran_fun(r1_dse_bayes) %>% regtab_style_fun()
```


# Country as fixed effect

## Table S29 (Spiritual Events)

```{r}
r2_spev <- lm(spev_score ~ abs_score * country,
              data = d3 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r2_spev)
```

```{r}
regtab_fun(r2_spev, std_beta = T, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```

## Table S30 (Daily Spiritual Experiences)

```{r}
r2_dse <- lm(dse_score ~ abs_score * country,
             data = d3 %>% mutate_at(vars(ends_with("_score")), scale))
```

```{r}
rsquared(r2_dse)
```

```{r}
regtab_fun(r2_dse, std_beta = T, por_name = "Porosity Scale") %>% 
  regtab_style_fun(row_emph = 2)
```


# Other analyses

## Primary analyses, by country (Supplemental Information, p. 12)

### Spiritual Events

```{r}
r1_spev_us <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "US") %>%
                   mutate_at(vars(ends_with("_score")), scale))

r1_spev_gh <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "Ghana") %>%
                   mutate_at(vars(ends_with("_score")), scale))

r1_spev_th <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "Thailand") %>%
                   mutate_at(vars(ends_with("_score")), scale))

r1_spev_ch <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "China") %>%
                   mutate_at(vars(ends_with("_score")), scale))

r1_spev_vt <- lm(spev_score ~ abs_score,
                 data = d3 %>% 
                   filter(country == "Vanuatu") %>%
                   mutate_at(vars(ends_with("_score")), scale))
```

```{r}
bind_rows(regtab_fun(r1_spev_us) %>% mutate(Country = "US"),
          regtab_fun(r1_spev_gh) %>% mutate(Country = "Ghana"),
          regtab_fun(r1_spev_th) %>% mutate(Country = "Thailand"),
          regtab_fun(r1_spev_ch) %>% mutate(Country = "China"),
          regtab_fun(r1_spev_vt) %>% mutate(Country = "Vanuatu")) %>%
  select(Country, everything()) %>%
  regtab_style_fun(row_emph = seq(2, 10, 2)) %>%
  collapse_rows(1)
```

### Daily Spiritual Experiences

```{r}
r1_dse_us <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "US") %>%
                  mutate_at(vars(ends_with("_score")), scale))

r1_dse_gh <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "Ghana") %>%
                  mutate_at(vars(ends_with("_score")), scale))

r1_dse_th <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "Thailand") %>%
                  mutate_at(vars(ends_with("_score")), scale))

r1_dse_ch <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "China") %>%
                  mutate_at(vars(ends_with("_score")), scale))

r1_dse_vt <- lm(dse_score ~ abs_score,
                data = d3 %>% 
                  filter(country == "Vanuatu") %>%
                  mutate_at(vars(ends_with("_score")), scale))
```

```{r}
bind_rows(regtab_fun(r1_dse_us) %>% mutate(Country = "US"),
          regtab_fun(r1_dse_gh) %>% mutate(Country = "Ghana"),
          regtab_fun(r1_dse_th) %>% mutate(Country = "Thailand"),
          regtab_fun(r1_dse_ch) %>% mutate(Country = "China"),
          regtab_fun(r1_dse_vt) %>% mutate(Country = "Vanuatu")) %>%
  select(Country, everything()) %>%
  regtab_style_fun(row_emph = seq(2, 10, 2)) %>%
  collapse_rows(1)
```

