---
title: "Study 3"
subtitle: "Luhrmann, Weisman, et al."
output: 
  html_notebook:
    toc: true
    toc_float: true
---

In Study 3, college undergraduates completed a survey consisting of one measure of absorption (the Absorption scale) and two measures of spiritual experience (a “Spiritual Events” inventory based on Studies 1 and 2; and a modified version of the Daily Spiritual Experiences scale). 

This notebook contains all of the analyses for Study 3 (revised July 2020).

```{r, message = F}
source("../scripts_general/dependencies.R")
source("../scripts_general/custom_funs.R")
source("../scripts_general/var_recode_contrast.R")
source("../scripts_general/data_load.R")
```


# Demographics (Table S16)

```{r}
d3_demo <- d3 %>% select(-contains("score")) %>% 
  mutate(male = ifelse(grepl("male", tolower(subject_gender)) &
                         !grepl("female", tolower(subject_gender)), 1, 0),
         female = ifelse(grepl("female", tolower(subject_gender)), 1, 0),
         subject_age = ifelse(subject_age > 120, NA_real_, subject_age),
         subject_religion = case_when(
           subject_religion %in% 
             c("christian", "(seventh day adventist) youth", "a.o.g.", "anglican",
               "anglicanism", "aog", "aog assemblies of god", 
               "agos, assemblies of god", "assemblies of god",
               "c.m.c presbyterian", "christian - ame (google it!)",
               "christian: anglican", "christian: catholic", 
               "christian: non specific", "christian: non-specific",
               "christian: protestant mainline", "christianity",
               "christianity: non specific", "church of christ",
               "coptic orthodox christian",
               "family worship ark healing ministry",
               "kingdom citizenship of god", "living water", "ntm",
               "pentecostal", "presbyterian", "presbyterian (illegible)",
               "protestant", "s.d.a.", "sda", "sda (seventh day adventist)",
               "seven day adventist", "seventh day adventist", 
               "seventh day adventist church", "sunday keeper",
               "word christian fellowship") ~ "Christian",
           subject_religion %in% 
             c("buddhist", "dge-lugs-pa (buddhist sect)", "sanqi buddhism",
               "some values of buddhism", "buddha temple", "buddha temples",
               "buddha temples & ancestral hall", "buddhist temples") ~ "Buddhist",
           # subject_religion %in% 
           #   c("Family - Orthodox Jew / Jewish",
           #     "Judaism", "Orthodox Jewish") ~ "Jewish",
           subject_religion %in%
             c("muslim") ~ "Muslim",
           # subject_religion %in% 
           #   c("Hinduism") ~ "Hindu",
           grepl("agnost", tolower(subject_religion)) |
             grepl("atheis", tolower(subject_religion)) |
             grepl("don't", tolower(subject_religion)) |
             grepl("none", tolower(subject_religion)) |
             tolower(subject_religion) %in% 
             c("n/a", "no", "no religion", "not really") ~ "Agnostic/Atheist",
           subject_religion %in% c("missing data", "mdata", "NA") |
             is.na(subject_religion) ~ "Missing data",
           TRUE ~ "Other"),
         agnostic_atheist = (subject_religion == "Agnostic/Atheist"),
           buddhist = (subject_religion == "Buddhist"),
           christian = (subject_religion == "Christian"),
           muslim = (subject_religion == "Muslim"),
           other = (subject_religion == "Other"),
         missing = (subject_religion == "Missing data"))
```

```{r}
d3_demo %>%
  group_by(country) %>%
  summarise(n = n(),
            age_range = paste0(min(subject_age, na.rm = T), "-",
                               max(subject_age, na.rm = T)),
            mean_age = mean(subject_age, na.rm = T),
            percent_male = mean(male, na.rm = T),
            percent_female = mean(female, na.rm = T),
            percent_affr = mean(subject_afford, na.rm = T),
            mean_ses = mean(subject_ses, na.rm = T),
            mean_religiosity = mean(subject_religiosity, na.rm = T),
            percent_christian = mean(christian, na.rm = T),
            percent_agnostic_atheist = mean(agnostic_atheist, na.rm = T),
            percent_buddhist = mean(buddhist, na.rm = T),
            percent_muslim = mean(muslim, na.rm = T),
            percent_other = mean(other, na.rm = T),
            percent_missing = mean(missing, na.rm = T)) %>%
  ungroup() %>%
  # mutate_at(vars(starts_with("mean_")), funs(format(round(., 2), nsmall = 2))) %>%
  mutate_at(vars(starts_with("percent_")),
            funs(paste0(round(. * 100), "%"))) %>%
  rename(Country = country, 
         `Age range` = age_range, `Mean age` = mean_age,
         `% male` = percent_male, `% female` = percent_female,
         `% can afford` = percent_affr,
         `% Christian` = percent_christian, 
         `% Agnostic/Atheist` = percent_agnostic_atheist, 
         `% Buddhist` = percent_buddhist, 
         `% Muslim` = percent_muslim, 
         `% Other` = percent_other,
         `[% Missing data]` = percent_missing,
         `Mean SES` = mean_ses, `Mean religiosity` = mean_religiosity) %>%
  mutate(Country = factor(Country, levels = levels_country)) %>%
  arrange(Country) %>%
  select(Country, n, `Age range`, `Mean age`, `% male`, `% female`,
         `Mean religiosity`,
         `% Christian`, `% Buddhist`, `% Muslim`, `% Other`, `% Agnostic/Atheist`,
         `[% Missing data]`,
         `% can afford`, `Mean SES`) %>%
  kable(digits = 2, align = c(rep("l", 2), rep("r", ncol(.) - 2))) %>%
  kable_styling(font_size = 16) # %>%
# collapse_rows(1:2)
```


# Regression analyses (Tables S31-S35)

## Setup

```{r}
# dataframe with variable names optimized for stargazer tables
d3_fortab <- d3 %>%
  mutate_at(vars(ends_with("_score"), subject_age), scale) %>%
  mutate(subject_gender = factor(subject_gender, 
                                 levels = c("female", "male"))) %>%
  rename("Spiritual Events" = "spev_score",
         "Daily Spiritual Experiences" = "dse_score",
         "Absorption" = "abs_score",
         "Country" = "country",
         "Gender" = "subject_gender",
         "Age" = "subject_age")
```

```{r}
# set contrasts
contrasts(d3_fortab$Country) <- cbind(": Gh." = c(-1, 1, 0, 0, 0),
                                      ": Th." = c(-1, 0, 1, 0, 0),
                                      ": Ch." = c(-1, 0, 0, 1, 0),
                                      ": Va." = c(-1, 0, 0, 0, 1))
contrasts(d3_fortab$Gender) <- cbind(": male" = c(-1, 1))
```

```{r}
# show contrasts
cat("Country\n"); contrasts(d3_fortab$Country)
cat("Gender\n"); contrasts(d3_fortab$Gender)
```

## Group differences

### Table S31. Study 3, Spiritual Events, Daily Spiritual Experience, and Absorption: group differences

```{r}
r01_spev <- lm(`Spiritual Events` ~ Country,
               data = d3_fortab)
r02_spev <- lm(`Spiritual Events` ~ Country 
               + Gender + Age, 
               data = d3_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r01_spev)
summary(r02_spev)
```

```{r}
r01_dse <- lm(`Daily Spiritual Experiences` ~ Country,
              data = d3_fortab)
r02_dse <- lm(`Daily Spiritual Experiences` ~ Country 
              + Gender + Age, 
              data = d3_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r01_dse)
summary(r02_dse)
```

```{r}
r01_abs <- lm(`Absorption` ~ Country,
              data = d3_fortab)
r02_abs <- lm(`Absorption` ~ Country 
              + Gender + Age, 
              data = d3_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r01_abs)
summary(r02_abs)
```

```{r, results = "hide"}
table_s31 <- stargazer(r01_spev, r02_spev, r01_dse, r02_dse, r01_abs, r02_abs, 
                       type = "html",
                       ci = T,
                       report = c("vcsp"),
                       digits = 2,
                       digits.extra = 1000,
                       omit.table.layout = "n",
                       # dep.var.labels.include = F,
                       dep.var.caption = "",
                       single.row = T)

cat(sub_interact_fun(table_s31),
    file = "./stargazer_tables/table_s31.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s31.html")
```

## Relationships

### Table S32. Study 3, Spiritual Events and Daily Spiritual Experience: relationships with Absorption (sample as fixed effect)

```{r}
r03_spev <- lm(`Spiritual Events` ~ `Absorption`,
               data = d3_fortab)

r04_spev <- lm(`Spiritual Events` ~ Country * `Absorption`,
               data = d3_fortab)

r05_spev <- lm(`Spiritual Events` ~ Country * `Absorption`
               + Gender + Age,  
               data = d3_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r03_spev)
summary(r04_spev)
summary(r05_spev)
```

```{r}
r03_dse <- lm(`Daily Spiritual Experiences` ~ `Absorption`,
              data = d3_fortab)

r04_dse <- lm(`Daily Spiritual Experiences` ~ Country * `Absorption`,
              data = d3_fortab)

r05_dse <- lm(`Daily Spiritual Experiences` ~ Country * `Absorption`
              + Gender + Age,  
              data = d3_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r03_dse)
summary(r04_dse)
summary(r05_dse)
```

```{r, results = "hide"}
table_s32 <- stargazer(r03_spev, r04_spev, r05_spev, r03_dse, r04_dse, r05_dse, 
                       type = "html",
                       ci = T,
                       report = c("vcsp"),
                       digits = 2,
                       digits.extra = 1000,
                       omit.table.layout = "n",
                       order = c("^Absorption$"),
                       # dep.var.labels.include = F,
                       dep.var.caption = "",
                       single.row = T)

cat(sub_interact_fun(table_s32), 
    file = "./stargazer_tables/table_s32.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s32.html")
```

### Table S33. Study 3, Spiritual Events and Daily Spiritual Experience: relationships with Absorption (sample as random effect)

```{r}
r06_spev <- lmer(`Spiritual Events` ~ 1 
                 + (1 | Country),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d3_fortab)

r07_spev <- lmer(`Spiritual Events` ~ `Absorption` 
                 # + (1 + `Absorption` | Country), # perfectly correlated ranfx
                 + (1 | Country),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d3_fortab)

r08_spev <- lmer(`Spiritual Events` ~ `Absorption`
                 + Gender + Age 
                 # + (1 + `Absorption` + Gender + Age | Country), # perfectly correlated ranfx
                 # + (1 + `Absorption` | Country), # perfectly correlated ranfx
                 + (1 | Country),
                 control = lmerControl(optimizer = "bobyqa"),
                 data = d3_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r06_spev)
summary(r07_spev)
summary(r08_spev)
```

```{r}
r06_dse <- lmer(`Daily Spiritual Experiences` ~ 1 
                + (1 | Country),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_fortab)

r07_dse <- lmer(`Daily Spiritual Experiences` ~ `Absorption` 
                # + (1 + `Absorption` | Country), # perfectly correlated ranfx
                + (1 | Country),
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_fortab)

r08_dse <- lmer(`Daily Spiritual Experiences` ~ `Absorption`
                + Gender + Age 
                # + (1 + `Absorption` + Gender + Age | Country), 
                # + (1 + `Absorption` | Country),
                + (1 | Country), # use this for comparsion with spev
                control = lmerControl(optimizer = "bobyqa"),
                data = d3_fortab)
```

```{r, include = F}
# run manually to check convergence
summary(r06_dse)
summary(r07_dse)
summary(r08_dse)
```

```{r, results = "hide"}
table_s33 <- stargazer(r06_spev, r07_spev, r08_spev, r06_dse, r07_dse, r08_dse,
                       type = "html",
                       ci = T,
                       report = c("vcsp"),
                       digits = 2,
                       digits.extra = 0800,
                       omit.table.layout = "n",
                       order = c("^`Absorption`$"),
                       # dep.var.labels.include = F,
                       dep.var.caption = "",
                       single.row = T)

cat(sub_interact_fun(table_s33), 
    file = "./stargazer_tables/table_s33.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s33.html")
```

```{r}
rsq_table_fun(list(r06_spev, r07_spev, r08_spev, r06_dse, r07_dse, r08_dse))
```

### Table S34. Study 3, Spiritual Events: relationships with Absorption by country

```{r}
r09_us_spev <- lm(`Spiritual Events` ~ `Absorption`,
                  data = d3_fortab %>% 
                    filter(Country == "US") %>%
                    mutate_at(vars(`Spiritual Events`, `Absorption`),
                              ~ scale(.)))

r09_gh_spev <- lm(`Spiritual Events` ~ `Absorption`,
                  data = d3_fortab %>% 
                    filter(Country == "Ghana") %>%
                    mutate_at(vars(`Spiritual Events`, `Absorption`),
                              ~ scale(.)))

r09_th_spev <- lm(`Spiritual Events` ~ `Absorption`,
                  data = d3_fortab %>% 
                    filter(Country == "Thailand") %>%
                    mutate_at(vars(`Spiritual Events`, `Absorption`),
                              ~ scale(.)))

r09_ch_spev <- lm(`Spiritual Events` ~ `Absorption`,
                  data = d3_fortab %>% 
                    filter(Country == "China") %>%
                    mutate_at(vars(`Spiritual Events`, `Absorption`),
                              ~ scale(.)))

r09_vt_spev <- lm(`Spiritual Events` ~ `Absorption`,
                  data = d3_fortab %>% 
                    filter(Country == "Vanuatu") %>%
                    mutate_at(vars(`Spiritual Events`, `Absorption`),
                              ~ scale(.)))
```

```{r, include = F}
# run manually to check convergence
summary(r09_us_spev)
summary(r09_gh_spev)
summary(r09_th_spev)
summary(r09_ch_spev)
summary(r09_vt_spev)
```

```{r, results = "hide"}
table_s34 <- stargazer(r09_us_spev, r09_gh_spev, r09_th_spev, r09_ch_spev, r09_vt_spev, 
                       type = "html",
                       ci = T,
                       report = c("vcsp"),
                       digits = 2,
                       digits.extra = 1000,
                       omit.table.layout = "n",
                       order = c("^`Absorption`$"),
                       # dep.var.labels.include = F,
                       dep.var.caption = "",
                       single.row = T)

cat(sub_interact_fun(table_s34), 
    file = "./stargazer_tables/table_s34.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s34.html")
```

### Table S35. Study 3, Daily Spiritual Experience: relationships with Absorption by country

```{r}
r09_us_dse <- lm(`Daily Spiritual Experiences` ~ `Absorption`,
                 data = d3_fortab %>% 
                   filter(Country == "US") %>%
                   mutate_at(vars(`Daily Spiritual Experiences`, `Absorption`),
                             ~ scale(.)))

r09_gh_dse <- lm(`Daily Spiritual Experiences` ~ `Absorption`,
                 data = d3_fortab %>% 
                   filter(Country == "Ghana") %>%
                   mutate_at(vars(`Daily Spiritual Experiences`, `Absorption`),
                             ~ scale(.)))

r09_th_dse <- lm(`Daily Spiritual Experiences` ~ `Absorption`,
                 data = d3_fortab %>% 
                   filter(Country == "Thailand") %>%
                   mutate_at(vars(`Daily Spiritual Experiences`, `Absorption`),
                             ~ scale(.)))

r09_ch_dse <- lm(`Daily Spiritual Experiences` ~ `Absorption`,
                 data = d3_fortab %>% 
                   filter(Country == "China") %>%
                   mutate_at(vars(`Daily Spiritual Experiences`, `Absorption`),
                             ~ scale(.)))

r09_vt_dse <- lm(`Daily Spiritual Experiences` ~ `Absorption`,
                 data = d3_fortab %>% 
                   filter(Country == "Vanuatu") %>%
                   mutate_at(vars(`Daily Spiritual Experiences`, `Absorption`),
                             ~ scale(.)))
```

```{r, include = F}
# run manually to check convergence
summary(r09_us_dse)
summary(r09_gh_dse)
summary(r09_th_dse)
summary(r09_ch_dse)
summary(r09_vt_dse)
```

```{r, results = "hide"}
table_s35 <- stargazer(r09_us_dse, r09_gh_dse, r09_th_dse, r09_ch_dse, r09_vt_dse, 
                       type = "html",
                       ci = T,
                       report = c("vcsp"),
                       digits = 2,
                       digits.extra = 1000,
                       omit.table.layout = "n",
                       order = c("^`Absorption`$"),
                       # dep.var.labels.include = F,
                       dep.var.caption = "",
                       single.row = T)

cat(sub_interact_fun(table_s35), 
    file = "./stargazer_tables/table_s35.html")
```

```{r}
htmltools::includeHTML("./stargazer_tables/table_s35.html")
```

